%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%  LA BIBLIOGRAFÍA %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{999}

\bibitem{mckeever_course_2022}
McKeever, Stephen W. S. (2022). \textit{A course in luminescence measurements and analyses for radiation dosimetry}. Wiley. ISBN 978-1-119-64689-1.

\bibitem{arenas_study_nodate}
F.~J.~F. Arenas, ``Study on photo-ionization cross-sections through the simulation of the behaviour of crystalline materials used in dosimetry,'' unpublished undergraduate thesis.


\bibitem{brey}
J.~J. Brey Abalo, \emph{Mecánica estadística}, 1a ed., 6a reimp. Madrid: Universidad Nacional de Educación a Distancia, 2020. 
Colaboradores: J.~de la Rubia Pacheco y J.~de la Rubia Sánchez. 
ISBN: 978-84-362-4572-1. 

\bibitem{benavente_LiF}
J.~F. Benavente, J.~M. Gómez-Ros, and A.~M. Romero, ``Numerical analysis of the irradiation and heating processes of thermoluminescent materials,'' \textit{Radiation Physics and Chemistry}, vol.~170, p. 108671, May 2020. doi: 10.1016/j.radphyschem.2019.108671.


\bibitem{lif} Y.~S. Horowitz, L.~Oster, and H.~Datz, The thermoluminescence dose response and other characteristics of the high-temperature TL in LiF:Mg,Ti (TLD-100), \textit{Radiation Protection Dosimetry}, vol. 124, no. 2, pp. 191--205, Jun. 2007, doi: 10.1093/rpd/ncm241.

\bibitem{massillon-jl_role_nodate}
G.~Massillon-JL, C.~S.~N. Johnston, and J.~Kohanoff, ``On the role of magnesium in {LiF}:{Mg},{Ti} thermoluminescent dosimeter,'' \emph{Journal of Physics: Condensed Matter}, vol.~30, no.~12, p. 125701, 2018. doi: 10.1088/1361-648X/aaee62.

\bibitem{bransden_atomics}
B.~H. Bransden and C.~J. Joachain, \emph{Physics of Atoms and Molecules}, 2nd ed. Harlow, England: Pearson Education, 2003.

\bibitem{horowitz_thermoluminescence_2007}
Y.~S. Horowitz, L.~Oster, and H.~Datz, ``The thermoluminescence dose response and other characteristics of the high-temperature {TL} in {LiF}:{Mg},{Ti} ({TLD}-100),'' \emph{Radiation Protection Dosimetry}, vol.~124, no.~2, pp. 191--205, Jun. 2007. doi: 10.1093/rpd/ncm241.

\bibitem{freq_factor1}
Halimi Mokhtar, Dahane Kadri, and Abdelmalek Mokeddem,
"Simulation of the experimental thermal cleaning procedure in LiF:Mg,Ti and investigation of the origin of the first-order kinetics of its peaks,"
\textit{Modern Physics Letters B}, vol. 29, no. 35, p. 1550226, Dec. 2015, doi:10.1142/S0217984915502267.

\bibitem{mckeever_1995}
S.~W.~S. McKeever, \emph{Thermoluminescence of Solids}. Cambridge University Press, 1985. doi: 10.1017/CBO9780511564991.



\end{thebibliography}